%-------------------------
% Resume in Latex
% Author : Shailesh
% License : MIT
%------------------------

\documentclass[letterpaper,10.8pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fontawesome}

\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}



\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.52in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1in}


\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6.09pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
{\fontfamily{bch}\selectfont

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Alok Raj}}\\
  {\faPhone {  +91-8709414158}} & \href{https://www.linkedin.com/in/loki-silvres/}{\faLinkedinSquare  {  Alok Raj}} \\
  \href{https://github.com/loki-silvres} {\faGithubSquare { Github }}  \href{https://loki-silvres.github.io/} {\faGithubSquare {  Website}} & \href{mailto:alok9360@gmail.com}{\small\faEnvelopeO { alok9360@gmail.com} }\\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Technology, (IIT ISM) Dhanbad}{Dhanbad, India}
      {Bachelors of Technology in Computer Science and Engineering; CGPA: 8.70 / 10.00 or 3.48 / 4.00 }{Class of 2026}
      
	   
	    
    \resumeSubheading
      {BR DAV Public School}{Begusarai, India}
      {High School(12th);  Percentage: 97.2\%
      }{Class of 2022}
    \resumeSubHeadingListEnd





%-----------EXPERIENCE-----------------
\section{Research Experience}
  \resumeSubHeadingListStart
      \resumeSubheading
		{Undergraduate Research Internship}{Remote}
		{Under   {\href{https://scholar.google.co.in/citations?user=cVdB1iwAAAAJ&hl=en}{Prof. G.C. Nandi}} \& {\href{https://scholar.google.com/citations?user=6tiiQtgAAAAJ&hl=en}{Andrew Melnik}}}{Dec 2024 - Present}
		\resumeItemListStart
        \resumeItem{Project}{Using state of the art foundation models(VLMs \& LLMs) to solve robotic manipulation problems.}
            \begin{description}[font=$\bullet$]
                \item {Working on precise manipulation in indoor environment relying on robot vision.}
                \end{description}
    \resumeItemListEnd

  
    \resumeSubheading
    {\href{https://www.clutterbot.com/}{Clutterbot Technologies}}{Bangalore, India}
    {Machine Learning Intern}{May 2024 - July 2024}
    \resumeItemListStart
        \resumeItem{Project}
          {Modernizing Object Detection with Distillation and Curriculum Learning}
        \resumeItem{Description}{}
          \begin{description}[font=$\bullet$]
            \item {Self-Training, using \href{https://arxiv.org/abs/2211.12860}{Co-DETR}, to expand the dataset with unannotated images.}
            \item {Curriculum learning trained \href{https://arxiv.org/abs/2211.15444}{DAMO-YOLO-M}, distilled to \href{https://arxiv.org/abs/2211.15444}{DAMO-YOLO-Tiny }for robot deployment.}
            \item {Improved mAP50 from 34\% to 42\% and evaluated performance with \href{https://arxiv.org/abs/2008.08115} {TIDE}.}
            \item {Deployed on robot using Nvidia DeepStream and integrated with ROS2.}
            \end{description}
      \resumeItemListEnd

     \resumeSubheading
    {\href{https://nvcti.iitism.ac.in/}{NVCTI, IIT(ISM)}}{Dhanbad, India}
    {Minor in Product Development Internship}{Feb 2024 - Jan 2025}
    \resumeItemListStart
        \resumeItem{Project}
          {Automating the process of road-marking with Computer Vision and Robotics.}
        \resumeItem{Description}{}
          \begin{description}[font=$\bullet$]
            \item {Designed a lane detection algorithm to guide the robot on roads.}
            \item {Created with a robot prototype for testing of effective lane following.}
            \item {Incorporated a spraying mechanism for marking roads.}
            \end{description}
      \resumeItemListEnd

    \resumeSubheading
    {\href{https://www.aduza.in/about-us/}{Robotics and Automation Lab, IIT (ISM)} \normalfont\color{blue}\href{https://youtu.be/RTfxgl5l3NM}{[video]}}{Dhanbad, India}
    {Research Intern: Under   {\href{https://scholar.google.com/citations?user=T1LKSLwAAAAJ&hl=en}{Prof. Arun Dayal Udai}}}{December 2023}
    \resumeItemListStart
        \resumeItem{Project}
          {Development of in-house Quadrupedal Robot for Mining Application.}
        \resumeItem{Work on Quadrupedal Robot}{}
          \begin{description}[font=$\bullet$]
            \item {Developed ROS based framework for a in-house developed Quadrupedal Robot. }
            \item {Reinforcement Learning based control policy.}
            \item {Hardware testing of locomotion controller.}
            \end{description}
    

      \resumeItemListEnd

     

\resumeSubHeadingListEnd

%-----------Projects-----------------
\section{Selected Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Mobile-Swarm-Navigation \color{blue} \normalfont \fontfamily{pcr} \href{https://drive.google.com/drive/folders/1R-KmugCW5OYquV0uMlaHNyM6oqgc6VKU}{[video folder]} \color{blue} \normalfont \fontfamily{pcr} \href{https://github.com/Loki-Silvres/Mobile-Swarm-Navigation}{[code]}} {}
    {Inter-IIT Tech Meet 13.0 - BharatForge}{Nov 2024 - Dec 2024}
          \begin{description}[font=$\cdot$]
            \item {\textbf{Project}: Create a \href{https://interiit-tech.com/wp-content/uploads/2024/11/BharatForge_MidPrep_InterIIT_TechMeet.pdf}{Centralised Intelligence for Dynamic Swarm Navigation}.}
            \item {Scalable ROS2 based robot swarm for autonomous exploration and navigation in a dynamic environment.}
            \item {Dynamic semantic environmental mapping with Instance Segmentation and Stereo Depth.}
            \item {Semantic database management system for task allocation for the swarm.}
            \end{description}

    \resumeSubheading
    {Autonomous Driving NXP-B3RB Buggy \color{blue} \normalfont \fontfamily{pcr} \href{https://loki-silvres.github.io/projects/1_project/}{[link]}}{}
    {NXP-AIM Self Driving Car Design Challenge: Under {\href{https://scholar.google.co.in/citations?user=4Uc5kc0AAAAJ&hl=en}{Prof. Subhrangsu Mandal}}}{Aug 2024 -  Oct 2024}
          \begin{description}[font=$\cdot$]
            \item {Developed an autonomous driving system, for a B3RB-buggy, achieving a 1:42 (min:sec) track time.}
            \item {Integrated LiDAR and camera for lane detection, obstacle avoidance, and traffic sign recognition.}
            \item {Trained YOLOv5s, optimized with INT8 quantization for NPU, achieving real-time 7 Hz inference.}
            \item {Utilized a mini computer running ROS2 for onboard processing and control.}
            \end{description}
  
    \resumeSubheading
    {Hologlyph Bots \color{blue} \normalfont \fontfamily{pcr} \href{https://www.youtube.com/watch?v=puT0LCRGoLM}{[video]} 
    \color{blue} \normalfont \fontfamily{pcr} \href{https://github.com/Loki-Silvres/Hologlyph-Bots}{[code]}} {}
    {E-Yantra 2023}{Aug 2023 -  Jan 2024}
          \begin{description}[font=$\cdot$]
            \item {Simulated a 3-bot swarm in Gazebo with overhead camera-based arena monitoring.}
            \item {Designed and 3D-printed bots in SolidWorks with three design iterations.}
            \item {Integrated inverse kinematics for a 3-wheeled holonomic drive using servos.}
            \item {Implemented Aruco detection for pen pose tracking in the arena.}
            \item {Developed PID control with camera feedback; used ESP-32 as a ROS2 node via Micro-ROS.}
            \end{description}


    \vspace{-30pt}
    \resumeSubHeadingListEnd
    %--------PROGRAMMING SKILLS------------
    \section{Skills}
    	\resumeSubHeadingListStart
     
    	\resumeSubItem
     {Programming}
     {C++, Python, MATLAB, Linux, Git, SQL, SSH}
     
    	\resumeSubItem
     {Simulation/Visualization}
     {Isaac Gym, Gazebo, RViz, CoppeliaSim, Mujoco, Sapien}
    
     \resumeSubItem
     {Frameworks/Libraries}
     {ROS/ROS2, RViz, PyTorch, OpenCV, Matplotlib}
     
     \resumeSubItem
     {Hardware}
     {Yashkawa Arm, Nvidia Jetson, Depth Camera, 2D LIDAR, Dynamixel Actuators, RaspberryPi}
    
    \resumeSubHeadingListEnd
    %-----------Coursework-----------------
    \section{Relevant Coursework}
        \resumeSubHeadingListStart

    	 \resumeSubItem
         {Mechatronics}
         {Engineering Mechanics, Analog Interface Electronics}
        
         \resumeSubItem
         {Software}
         {Reinforcement Learning, Self-Supervised Learning, Convolutional Neural Networks, Transformers, Data Structure \& Algorithm}
        
    \resumeSubHeadingListEnd

    %-----------Awards-----------------
    \section{Honors and Awards}
    \begin{description}[font=$\bullet$]
    \item {6th Position: InterIIT Tech Meet 13.0 for Rigbettlelabs} 
    \item {Winner: NXP-AIM Regional Finale}
    \item {3rd Position: Robowars(BattleBots) at TechKriti 2024 (Annual Tech Fest of IIT Kanpur)}
    \item {3rd Position: Robowars(BattleBots) at Concetto 2024 (Annual Tech Fest of IIT Dhanbad)}
    \item {Received the Excellent Academic Performance Award (AISSCE 2022).}
    \end{description}
    %-------------------------------------------

    %-----------Extra-Curricular-----------------
    \section{Extra-Curricular Activities}
    \begin{description}[font=$\bullet$]
    \resumeSubItem{Club Coordinator}{RoboISM - The official Robotics and AI club of IIT ISM Dhanbad. }
     \resumeSubItem{Joint Event Coordinator}{NVCTI - The innovation cell of IIT ISM Dhanbad. }
     \resumeSubItem{Hobbies}{Guitar, Chess, Badminton.}
    \end{description}
    %-------------------------------------------
    
}
\end{document}